My Cool Title

### 2019-05-04 paper.tex
Added some references, removed some todos

The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm\todo{cite} to solve the POMDP model 
The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{belloto2013} that exploits a uses a spatialised audio signal.
However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively\todo{cite} and adjust the sound source's pitch as a function of the waypoint's tilt angle. 
With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.

@@

The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.

>>>>

The difficulty of solving POMDPs is that the belief vector is a vector of continuous probability distributions with infinite combinations, making them very time-consuming or even impossible to solve exactly and we found this to be the case for our moderately-sized state space size and therefore opted to use an approximate method instead.
Multiple algorithms that solve POMDPs approximately have been proposed\todo{cite examples} and in this work we used the Point-Based Value Iteration (PBVI) algorithm~\cite{pineau2003point} to solve the POMDP model.
The PBVI algorithm speeds up the optimisation process by selecting a smaller subset of representative belief points from the belief function and tracking the values and derivatives of those points only. 
Using the PBVI algorithm, we generated a total of 15 policies, one for each target object.

@@

To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch as a function of the waypoint's tilt angle. 
A similar interface was used in~\cite{schauerte2012assistive}.
With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.

@@

The output from the POMDP model's training process is a policy file that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device during run-time by recording the device's previous search locations and previous waypoint positions, which is done by disretising the world into a $6\times6$ grid and setting the relevant grid unit's $v$ value.
Each grid square represents a \SI{35}{\degree} angular translation, encompassing a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while the observation parameter $o$ is generated by the object detector.
